\documentclass[draft=false
              ,paper=a4
              ,twoside=false
              ,fontsize=11pt
              ,headsepline
              ,BCOR10mm
              ,DIV11
              ]{scrbook}
\usepackage[english,ngerman]{babel}
%\usepackage[ngerman,english]{babel}
%% see http://www.tex.ac.uk/cgi-bin/texfaq2html?label=uselmfonts
\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage[latin1]{inputenc}
\usepackage{libertine}
\usepackage{pifont}
\usepackage{microtype}
\usepackage{textcomp}
\usepackage[english,refpage]{nomencl}
%\usepackage[german,refpage]{nomencl}
\usepackage{setspace}
\usepackage{makeidx}
\usepackage{listings}
\usepackage{natbib}
\usepackage[english,colorlinks=true]{hyperref}
%\usepackage[ngerman,colorlinks=true]{hyperref}
\usepackage{soul}

\usepackage{hawstyle}           %Mit Logo 
%\usepackage[printer]{hawstyle} %Ohne Logo

\usepackage{placeins}

\usepackage{wrapfig} %Bilder umfließen
\usepackage{graphicx}
\usepackage{floatflt,epsfig} 

\usepackage[nottoc]{tocbibind}

%% inputs
\input{Abstract.tex}
\input{Introduction.tex}
\input{EmbeddedReactiveSystems.tex}
\input{Cplusplus.tex}
\input{DesignPattern.tex}
\input{FactoryPattern.tex}
\input{StatePattern.tex}
\input{Conclusion.tex}
\input{Perspective.tex}

%% define some colors
\colorlet{BackgroundColor}{gray!20}
\colorlet{KeywordColor}{blue}
\colorlet{CommentColor}{black!60}
%% for tables
\colorlet{HeadColor}{gray!60}
\colorlet{Color1}{blue!10}
\colorlet{Color2}{white}

%% configure colors
\HAWifprinter{
  \colorlet{BackgroundColor}{gray!20}
  \colorlet{KeywordColor}{black}
  \colorlet{CommentColor}{gray}
  % for tables
  \colorlet{HeadColor}{gray!60}
  \colorlet{Color1}{gray!40}
  \colorlet{Color2}{white}
}{}
\lstset{%
  numbers=left,
  numberstyle=\tiny,
  stepnumber=1,
  numbersep=5pt,
  basicstyle=\ttfamily\small,
  keywordstyle=\color{KeywordColor}\bfseries,
  identifierstyle=\color{black},
  commentstyle=\color{CommentColor},
  backgroundcolor=\color{BackgroundColor},
  captionpos=b,
  fontadjust=true
}
\lstset{escapeinside={(*@}{@*)}, % used to enter latex code inside listings
        morekeywords={uint32_t, int32_t}
}
\ifpdfoutput{
  \hypersetup{bookmarksopen=false,bookmarksnumbered,linktocpage}
}{}

%% more fancy C++
\DeclareRobustCommand{\cxx}{C\raisebox{0.25ex}{{\scriptsize +\kern-0.25ex +}}}

\clubpenalty=10000
\widowpenalty=10000
\displaywidowpenalty=10000

% unknown hyphenations
\hyphenation{
}

%% recalculate text area
\typearea[current]{last}

\makeindex
\makenomenclature

\begin{document}
\selectlanguage{english}
%\selectlanguage{ngerman}

%%%%%
%% customize (see readme.pdf for supported values)
\HAWThesisProperties{Author={Lars Christian Schwensen}
                    ,Title={Eingebettete reaktive Systeme - Der Einfluss moderner C++ Standards auf ausgewählte Entwurfsmuster}
                    ,EnglishTitle={Embedded reactive systems - The impact of modern C++ standards on selected design patterns}
                    ,ThesisType={Bachelor thesis}
                    ,ExaminationType={Bachelorprüfung}
                    ,DegreeProgramme={Bachelor of Science Technische Informatik}
                    ,ThesisExperts={Prof. Dr. rer. nat. Stephan Pareigis \and Prof. Dr. Martin Becke}
                    ,ReleaseDate={04. April 2016}
                  }

%% title
\frontmatter

%% output title page
\maketitle

\onehalfspacing

%% add abstract pages
%% note: this is one command on multiple lines
\HAWAbstractPage
%% German abstract
{Reaktive Systeme, Eingebettete Systeme, C++11, C++14, Entwurfsmuster}%
{In diesem Dokument wird der Einfluss der Verwendung von mit C++11 und C++14 neu eingeführten Erweiterungen auf die in C++ implementierten Entwurfsmuster Fabrik Methoden Muster und Zustandsmuster untersucht und die Auswirkung von zeitlichem Verhalten, Speicherverbrauch und Code Qualität im direkten Vergleich zu etablierten Implementationsarten festgestellt.\vspace{30 mm}}
%% English abstract
{Reactive systems, Embedded systems, C++11, C++14, Design patterns}%
{Within this document the impact of the use of C++11 and C++14 facilities on the in C++ implemented design patterns factory method pattern and state pattern will be analysed to examine the effect on timing, memory consumption and code quality compared with the established ways of implementation.}

\newpage
\singlespacing

\tableofcontents
\newpage
%% enable if these lists should be shown on their own page
\listoftables
\listoffigures

\clearpage
\addcontentsline{toc}{chapter}{\lstlistlistingname}
\lstlistoflistings

%% main
\mainmatter
\onehalfspacing

%% -------------------------------------------- Begin here!--------------------
\Introduction
\EmbeddedReactiveSystems
\Cplusplus

\DesignPattern
\FactoryPattern
\StatePattern
\Clonclusion
\Perspective

%% appendix if used
%%\appendix
%%\typeout{===== File: appendix}
%%\include{appendix}

% bibliography and other stuff
\backmatter

\typeout{===== Section: literature}
%% read the documentation for customizing the style
\bibliographystyle{dinat}
\bibliography{sample}

\typeout{===== Section: nomenclature}
%% uncomment if a TOC entry is needed
%%\addcontentsline{toc}{chapter}{Glossar}
\renewcommand{\nomname}{Glossar}
\clearpage
\markboth{\nomname}{\nomname} %% see nomencl doc, page 9, section 4.1
\printnomenclature

%% index
\typeout{===== Section: index}
\printindex

\HAWasurency

\end{document}
